\section*{Experience}

\begin{itemize}
  \item \textbf{Lecturer in Information Security}, Royal Holloway, University of London \hfill Dec 2023--Present
  \begin{itemize}
    \item UG Lead - from 2025 
    \item responsible for IY3501 (Security Management), IY3821 (Information Security BSc Project), and IY4500 (Information Security MSci Project) - from 2023
    \item raised the attendance for IY3501 (Security Management) from 23\% to 70\% by creating a custom attendance tracking system
    \item raised the average grade IY3501 (Security Management) from 62\% to 69\%
    \item won Teaching Excellence Award for creating an interactive atmosphere in lectures
    \item published two collections of selected student work
    \item ethics reviewer and member working groups around curriculum design and assessment
  \end{itemize}

  \item \textbf{Founder and CEO}, eQuality Time \hfill Sep 2014--Sep 2023
  \begin{itemize}
    \item managed teams of up to 15 people 
    \item created and scaled the White Water Writers school intervention, which worked with over 100 schools, hospitals, and prisons, and enabled almost 3,000 people to publish their first novel.  
    \item won the £50,000 Nesta inclusive technology prize for our open source speech aid The Open Voice Factory 
    \item raised over £35,000 for sister charity Special Effect, as part of the Flowers For Turing event. 
  \item Created cybersecurity and media literacy programmes used in schools nationwide:
      \begin{itemize}
        \item \textit{Tightrope Project} (cybersecurity education): \textasciitilde2,000 annual downloads.
        \item \textit{Project Real} (fake news/misinformation): \textasciitilde3,500 annual downloads.
      \end{itemize}
  \end{itemize}

  \item \textbf{Research Assistant (PlanCompS)}, Royal Holloway, University of London \hfill Aug 2011--Sep 2014
  \begin{itemize}
    \item Focused on formal language specification and tool development for the PLanCompS project.
    \item Designed tools for validating specifications and generating prototype implementations.
  \end{itemize}

  \item \textbf{Teaching Fellow}, Royal Holloway, University of London \hfill Nov 2010--Apr 2011
  \begin{itemize}
    \item Led the masters course ‘People and Technology’ for the iCOM centre.
    \item Taught ‘Algorithms and Complexity’; received the college excellence teaching prize for 2010/2011. 
  \end{itemize}

  \item \textbf{Research Assistant}, University of Aberdeen \hfill Jan 2010--Oct 2010
  \begin{itemize}
    \item Designed and deployed wireless tracking systems in schools for a speech-aid enhancement project.
    \item Contributed to research publications and taught IT and game design courses.
  \end{itemize}

  \item \textbf{Analyst Programmer}, QCC Information Security \hfill May 2009--Oct 2009
  \begin{itemize}
    \item Developed tools in C# and JavaScript for digital forensic analysis.
    \item Gained hands-on experience with forensic evidence capture and mobile tracking.
  \end{itemize}

  \item \textbf{IT Tutor}, Royal Holloway, University of London \hfill Sep 2007--Jan 2010
  \begin{itemize}
    \item Delivered tailored IT training; specialised in ECDL for Health and Social Care students.
    \item Designed and led short courses; received the postgraduate tutor award for 2007/2008.
  \end{itemize}
\end{itemize}

